Windowed Developer Topic Analysis

### 2009-03-13 lda-paper.tex
abstract

\author{Abram Hindle and Michael Godfrey and Ric Holt \\
\{ahindle,migod,holt\}@cs.uwaterloo.ca\\
Software Architecture Group (SWAG)\\
University of Waterloo\\
}
\title{Temporal Developer Concept Witchery: Latent Dirichlet Allocation Applied to Revisions}

@@

>>>>

\author{Abram Hindle and Michael Godfrey and Ric Holt \\
\{ahindle,migod,holt\}@cs.uwaterloo.ca\\
Software Architecture Group (SWAG)\\
University of Waterloo\\
}
\title{Windowed Developer Topic Analysis}

@@

  At different times, developers focus on different topics and tasks
  during development.  These different topics and times of focus might
  be obvious to developers familar with the project, but other
  stakeholders, like managers, might be less aware of the topics of
  development. Imagine the scenario where developers had to deal with
  issues orthogonal to the features suggested, at the end of the
  iteration a manager would wonder where all the time went, the
  developers might have just blocked all sides issues in with features
  they were initially working on, they might not have noticed their
  focus had changed.  Currently it is difficult for stakeholders to
  audit what actually occurred and when certain features or topics
  were focussed on. We propose and provide a visualization of the
  changing development topics over time. Using
